\subsection{Modules}

SystemBurn is designed to run several different modules, or plans, simultaneously. These modules all do different types of calculations and stress different areas of the architecture. The user is able
to load new modules at any time so as to fine tune the load. The modules which are included in this release of SystemBurn are: 
\begin{description}
	\item[DGEMM size] A double precision matrix multiplication benchmark which will run to consume ``size'' bytes of memory.
	\item[RDGEMM size] A double precision rectangular matrix multiplication benchmark which will run to consume ``size'' bytes of memory.
	\item[LSTREAM size] Streaming integer vector operations run to consume ``size'' bytes of memory.
	\item[DSTREAM size] Streaming double precision floating point vector operations run to consume ``size'' bytes of memory.
	\item[LSTRIDE size] An integer load which accesses memory with changing stride, using ``size'' bytes of memory.
	\item[DSTRIDE size] A double precision floating point load which accesses memory with changing stride, using ``size'' bytes of memory.
	\item[FFT1D size] A 1 dimensional complex fast Fourier transform in a memory footprint of ``size'' bytes.
	\item[FFT2D size] A 2 dimensional complex fast Fourier transform in a memory footprint of ``size'' bytes.
	\item[GUPS size] Giga Updates Per Second - a random memory access benchmark on a table of ``size'' bytes. Note that ``size'' must be a power of 2, if it is not, it will be adjusted to the largest
	power of 2 which will fit within ``size'' bytes.
	\item[PV1 size]  A power hungry streaming computational algorithm on four arrays of 64bit values, which will operate with a memory footprint of ``size' bytes.
	\item[PV2 size]  A power hungry streaming computational algorithm on one array of 64bit values, which will operate with a memory footprint of ``size'' bytes. This load was tuned to a quadcore Intel
			``Nehalem'' processor, but may be suitable for loading multiple x86-64 cores until the memory system is saturated. It is intended to be run with a footprint large enough to require main
	                memory access.
	\item[PV3 size]  A power hungry streaming computational algorithm on one array of 64bit values, which will operate with a memory footprint of ``size'' bytes. This load was tuned to a quadcore AMD
		        ``Instabul'' processor, but may be suitable for loading multiple x86-64 cores until the memory system is saturated. It is intended to be run with a footprint large enough to require main
			memory access.
	\item[PV4 size]  A power hungry streaming computational algorithm on one array of 64bit values. It is intended to run in a smaller memory footprint which will be contained in L2 cache, not
	inducing main memory traffic. 
	\item[CBA size]  A bit-twiddling load which will run within ``size'' bytes of memory.
	\item[TILT niter]  A bit-twiddling load with a small memory footprint, ``niter'' iterations at a time.
	\item[DCUBLAS device count threads] A CUDA double precision load for GPUs. The load is sized automatically to memory available on the GPU. The GPU ``device'' number, the ``count''
	of iterations per pass, and the number of GPU ``threads'' to be used, may optionally be specified.  The defaults are device 0, count 8, and a thread count appropriate to the device hardware.
	\item[SCUBLAS device count threads] A CUDA single precision load for GPUs. The load is sized automatically to memory available on the GPU. The GPU ``device'' number, the ``count''
	of iterations per pass, and the number of GPU ``threads'' to be used, may optionally be specified.  The defaults are device 0, count 8, and a thread count appropriate to the device hardware.
	\item[WRITE megabytes string] A I/O load which writes ``megabytes'' to files with ``string'' as the basename (this can be a path).
	\item[SLEEP N] Puts a thread to sleep for N seconds at a time. 
\end{description}

Note: in most places a size in bytes is requested, the integer may have K, M, G, or T appended to indicate kilo, mega, giga, tera, (power of 2 based).
