\section{Vision}

Traditional benchmarks probe only a few of a machine's hardware features
at a time, which doesn't give a good overall feel for how the system acts
under all kinds of stress. Conversely, SystemBurn has been engineered to
place a system under composite stress. Under user-control, the induced
stress can be either purely synthetic, to stress the system's operating
envelope, or a composite load intended to provide some emulation of a real
application or suite of applications, to examine "typical" operating
conditions. SystemBurn was created to allow the user flexibility when
choosing which hardware components are to be stressed and how that is
to occur.

SystemBurn provides a capability for the creation and control
of multiple concurrent artificial system loads. These loads can be
used to test a system under a variety of stress states and to maintain
those stress states in a controlled fashion allowing for collection of
physical measurements of various parameters of interest on the system
and its environment, including but not limited to temperatures, air
flows, and power draws, both per node and for the overall environment.
These data sets can then be used to determine which loads cause the
most stress, in terms of component temperature, power drawn, heat
generated, etc. Thus, with purpose-crafted loads, the actual peak
run time power requirement and thermal load can be measured, providing
data for the assessment of sufficiency of power and cooling capacity and
the data required for the reallocation of power and cooling in excess
of the actual requirement, rather than relying on power and cooling
estimates from the vendor. From the data gathered using SystemBurn it
will be possible to compile power and temperature profiles for specific
tasks. These profiles have the potential to eventually trace the tasks
running on a machine simply by looking at the profiles. Through the use of
multiple load modules, each of which stress the system in a specific way,
it is possible to assemble loads representing an extreme system stress,
or loads which perform similarly to some single large application.

